%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
%\begin{filecontents*}{example.eps}
%%!PS-Adobe-3.0 EPSF-3.0
%%%BoundingBox: 19 19 221 221
%%%CreationDate: Mon Sep 29 1997
%%%Creator: programmed by hand (JK)
%%%EndComments
%gsave
%newpath
%  20 20 moveto
%  20 220 lineto
%  220 220 lineto
%  220 20 lineto
%closepath
%2 setlinewidth
%gsave
%  .4 setgray fill
%grestore
%stroke
%grestore
%\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{slashbox}     
\usepackage{subfigure}
\usepackage{breakcites}

%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Identifying Values to Express Emotions with a Non-Anthropomorphic Platform%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{Julian M. Angel-Fernandez         \and
        Andrea Bonarini %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Julian M. Angel-Fernandez \at
              Automation and Control Institute, Vienna University of Technology,\\ Karlsplatz 13, 1040 Vienna, Austria \\
              Tel.: +43-158801\\
              \email{julian.angel.fernandez@tuwien.ac.at}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Andrea Bonarini \at
              Andrea Bonarini, Dipartimento di Elettronica, Informazione e Bioingegneria,Politecnico di Milano,\\
              Piazza Leonardo da Vinci 32, 20133 Milan, Italy \\
              \email{andrea.bonarini@polimi.it}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor


\maketitle

\begin{abstract}
Social environments are intricate spaces where people behave in ways that are socially accepted. In a similar way, robots that interact with humans on a daily bases are expected to develop certain behaviours to be socially accepted by people. This creates the necessity to point out our attention on social presence of robots, to let humans feel comfortable with them. The straightest way to fulfill this is through imitation of humans' characteristics, such us body shape, behaviors and social characteristics. As a consequence many social robots have been built with anthropomorphic embodiment, which could include features to express emotions. Although anthropomorphic embodiment may support robot acceptance in interactive tasks, there are robots that not required anthropomorphic shape due to the nature of the tasks that they have to perform. As a consequence,  features not related with anthropomorphic embodiment should be exploited to support robot acceptance. This paper presents an experiment made to understand humans' perception of emotion given angular and linear velocity, body orientation, and movement direction. Therefore, a non-anthropomorphic platform was used in the experiments to let participants to focus on the desired features. Moreover a Likert questionnaire was used to measure participants' perception for different treatments. The Krippendorff's alpha agreement was used to create a top 10 table for each of the emotions listed in the questionnaire. The obtained results suggest values that could guide the implementation of the considered emotions in social robots.
\keywords{Human-Robot Interaction \and Emotion Expression \and Experiment \and Non-anthropomorphic Platform \and Emotions Expression with Non-anthropomorphic Platform}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\input{./Parts/Introduction}
\section{Emotional Models}
\input{./Parts/EmotionModels}
\section{Related Work}
\input{./Parts/Emotion_Projection}
\section{The System}
\label{sec:system}
\input{./Parts/Platform}
\section{Experimental Design}
\label{sec:experiment}
\input{./Parts/ExperimentDesign}
\section{Results}
\label{sec:result}
\input{./Parts/Results}
\section{Discussion}
\label{sec:discussion}
\input{./Parts/Discussion}
\section{Conclusions and Further Work}
\input{./Parts/Conclusion}
\bibliographystyle{spmpsci}
\bibliography{Bibliography,BibloNew,Biblography}

\end{document}
% end of file template.tex

